null_model

### 2021-03-24 analysis/01_filter_by_traits.Rmd
Clean up

#split into two different timeseries based on whether they're bird or mammal observations,
#remove years with too few species
mix_split <- biotime_traits %>%
  filter(study_id %in% mix_study) %>%
  mutate(rarefyid = if_else(class == "Aves", paste0(rarefyid, "_bird"), paste0(rarefyid, "_mamm"))) %>%
  group_by(rarefyid, year) %>% 
  filter(n_distinct(species) > 4)

>>>>

#split into two different timeseries based on whether they're bird or mammal observations,
#remove years with too few species
mix_split <- biotime_traits %>%
  filter(study_id %in% mix_study) %>%
  mutate(rarefyid = if_else(class == "Aves", paste0(rarefyid, "_bird"), paste0(rarefyid, "_mamm")),
         taxa = if_else(class == "Aves", "Birds", paste0(rarefyid, "Mammals"))) %>%
  group_by(rarefyid, year) %>% 
  filter(n_distinct(species) > 4)

### 2021-03-24 analysis/05_model_metrics.Rmd
Clean up

>>>>

Kitchen sink model
```{r}
all_model <- metrics %>%
  filter(metric %in%  c("FRic", "FEve", "FDiv", "S_int")) %>%
  group_nest(metric) %>%
  mutate(model = map(data, ~lmer(logvalue ~ year_scaled + taxa + realm + (year_scaled|study_id/rarefyID), 
                                 data = .x)))#,
  #          null_model = map(data, ~lmer(logvalue ~ (year_scaled|study_id/rarefyID), 
  #                                data = .x)),
  #          test = map2(model, null_model, anova),
  #          test_res = map(test, tidy),
  #          coef = map(model, tidy)
  #          ) %>% 
  # unnest(cols = c(test_res)) %>%
  # select(metric, model, coef, p.value) %>%
  # filter(!is.na(p.value)) %>%
  # unnest(cols = c(coef)) %>%
  # filter(term == "year_scaled") %>%
  # select(-c(effect, group, term, statistic))

### 2021-03-24 analysis/ts_null_model.Rmd
Clean up

Get sample dataframe
```{r}
future::plan(multiprocess)
sample_occurrence <- future_map(unique(biotime_traits$plot_id), get_plot_sample, data = biotime_traits, n = n) %>%
  bind_rows() %>%
  replace(is.na(.), 0)
```

>>>>

Get sample dataframe
```{r}
future::plan(multiprocess)
sample_occurrence <- future_map(unique(biotime_traits$rarefyid), get_plot_sample, data = biotime_traits, n = n) %>%
  bind_rows() %>%
  replace(is.na(.), 0)
```
